### 2024-10-16 base-rates.qmd
20241013 - specify heading
20241014 - reduce use of abbreviations
20241016 - render the figure caption as alt text

#### Example 3A {#sec-nateSilverExample3A}

@@

#### Example 3B {#sec-nateSilverExample3B}

@@

::: {#fig-probabilityNomogram}
![](images/probabilityNomogram.png){width=50%}

@@

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50%}

>>>>

#### Example 3A: The First Plane Hit the World Trade Center {#sec-nateSilverExample3A}

@@

#### Example 3B: The Second Plane Hit the World Trade Center {#sec-nateSilverExample3B}

@@

::: {#fig-probabilityNomogram}
![](images/probabilityNomogram.png){width=50%}\

@@

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50%}\

### 2024-10-16 causal-inference.qmd
20240815 - Simpson's paradox
20240816 - clean up references
20241016 - render the figure caption as alt text

::: {#fig-crossSectional}
![](images/Longitudinal-01.png){width=20%}

@@

::: {#fig-laggedAssociation}
![](images/Longitudinal-02.png)

@@

::: {#fig-laggedAssociationControlPriorLevels}
![](images/Longitudinal-03.png)

@@

::: {#fig-crossLaggedPanelModel}
![](images/Longitudinal-04.png)

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png){width=200%}

Example Where Failing to Control for a Variable (In This Case, Gender) Would Lead to False Inferences. In this example, the association between dosage and recovery probability is positive at the population level, but the association is negative among men and women separately. (Figure reprinted from @Kievit2013, Figure 1, p. 2. Kievit, R., Frankenhuis, W., Waldorp, L., & Borsboom, D. (2013). Simpson's paradox in psychological science: a practical guide. *Frontiers in Psychology*, *4*(513). [https://doi.org/10.3389/fpsyg.2013.00513](https://doi.org/10.3389/fpsyg.2013.00513))
:::

However, it can be problematic to control for variables indiscriminantly.
The use of [causal diagrams](#sec-causalDiagrams) can inform which variables are important to be included as control variables, and—just as important—which variables not to include as control variables, as described in @sec-causalDiagrams.

>>>>

::: {#fig-crossSectional}
![](images/Longitudinal-01.png){width=20%}\

@@

::: {#fig-laggedAssociation}
![](images/Longitudinal-02.png)\

@@

::: {#fig-laggedAssociationControlPriorLevels}
![](images/Longitudinal-03.png)\

@@

::: {#fig-crossLaggedPanelModel}
![](images/Longitudinal-04.png)\

@@

::: {#fig-simpsonParadox}
![](images/simpsonParadox.png){width=200%}\

Example Where Failing to Control for a Variable (In This Case, Gender) Would Lead to False Inferences. In this example, the association between dosage and recovery probability is positive at the population level, but the association is negative among men and women separately. (Figure reprinted from @Kievit2013, Figure 1, p. 2. Kievit, R., Frankenhuis, W., Waldorp, L., & Borsboom, D. (2013). Simpson's paradox in psychological science: A practical guide. *Frontiers in Psychology*, *4*(513). [https://doi.org/10.3389/fpsyg.2013.00513](https://doi.org/10.3389/fpsyg.2013.00513))
:::

However, it can be problematic to control for variables indiscriminantly [@Spector2010; @Wysocki2022].
The use of [causal diagrams](#sec-causalDiagrams) can inform which variables are important to be included as control variables, and—just as important—which variables not to include as control variables, as described in @sec-causalDiagrams.

### 2024-10-16 fantasy-football.qmd
20241016 - render the figure caption as alt text

![Video that Provides An Introduction to American Football. From: <https://www.youtube.com/watch?v=Ddwp1HyEFRE>.](images/football.mp4){width=100%}

@@

::: {#fig-footballFormation}
![](images/footballFormation.png)

@@

::: {#fig-footballField}
![](images/footballField.png){width=50%}

@@

![Video that Provides an Introduction to Fantasy Football. From: <https://www.youtube.com/watch?v=XhrBapdhLEc>.](images/fantasyFootball.mp4){width=100%}

>>>>

![Video that Provides An Introduction to American Football. From: <https://www.youtube.com/watch?v=Ddwp1HyEFRE>.](images/football.mp4){width=100%}\

@@

::: {#fig-footballFormation}
![](images/footballFormation.png)\

@@

::: {#fig-footballField}
![](images/footballField.png){width=50%}\

@@

![Video that Provides an Introduction to Fantasy Football. From: <https://www.youtube.com/watch?v=XhrBapdhLEc>.](images/fantasyFootball.mp4){width=100%}\

### 2024-10-16 index.qmd
20241016 - render the figure caption as alt text

![Creative Commons License](images/CC-BY.png){width=25% fig-align="left"}

@@

<!--
[![DOI](images/zenodo_doiBadge.png)](https://doi.org/10.5281/zenodo.6466589)
-->

>>>>

![Creative Commons License](images/CC-BY.png){width=25% fig-align="left"}\

@@

<!--
[![DOI](images/zenodo_doiBadge.png)](https://doi.org/10.5281/zenodo.6466589)\
-->

### 2024-10-16 multiple-regression.qmd
20241016 - render the figure caption as alt text

::: {#fig-regression}
![](images/regression.png)

@@

::: {#fig-regression}
![](images/multipleRegressionRSquared.png){width=50%}

@@

::: {#fig-regression}
![](images/multipleRegressionMulticollinearity.png){width=50%}

>>>>

::: {#fig-regression}
![](images/regression.png)\

@@

::: {#fig-regression}
![](images/multipleRegressionRSquared.png){width=50%}\

@@

::: {#fig-regression}
![](images/multipleRegressionMulticollinearity.png){width=50%}\
